\documentclass[a4paper,10pt]{article}

\usepackage[a4paper,top=0.45in,bottom=0.45in,left=0.5in,right=0.5in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\pagenumbering{gobble}

% ---------- Color ----------
\definecolor{linkblue}{HTML}{1a0dab}
\hypersetup{
    colorlinks=false,
    urlcolor=linkblue,
    linkcolor=linkblue
}

% ---------- Section Formatting ----------
\titleformat{\section}
{\color{linkblue}\bfseries\uppercase}
{}
{0pt}
{}
[\titlerule]

\setlist[itemize]{leftmargin=*, itemsep=2pt}

\begin{document}

% ===================== HEADER =====================
\begin{center}
    {\LARGE \textbf{Bharat Yadav}}\\
    Neemrana, Rajasthan, India \,|\, 
    \href{tel:+917011072551}{+91 7011072551} \,|\, 
    \href{mailto:yadav.bharatyadav007@gmail.com}{yadav.bharatyadav007@gmail.com} \,|\, 
    \href{https://www.linkedin.com/in/bharat-yadav-007bharat/}{linkedin.com/in/bharat-yadav-007bharat} \,|\, 
    \href{https://github.com/BharatYadav007}{github.com/BharatYadav007}
\end{center}

% ===================== SUMMARY =====================
\section*{SUMMARY}
Computer Science undergraduate with hands-on experience in \textbf{cybersecurity, system-level programming, and applied problem solving}. Contributed to \textbf{real-world cybercrime investigation tools} during a law-enforcement internship, working on OSINT automation, vulnerability assessment, and computer vision systems. Seeking internship roles in \textbf{Cybersecurity or Software Engineering} focused on building secure, scalable systems.

% ===================== TECHNICAL FOCUS =====================
\section*{TECHNICAL FOCUS}
\begin{itemize}
  \item Security-first mindset with exposure to \textbf{offensive and defensive techniques} through VAPT and OSINT workflows.
  \item Strong foundation in \textbf{core CS concepts}: data structures, operating systems, and system-level programming.
  \item Experience translating academic and theoretical concepts into \textbf{deployable investigative and automation tools}.
\end{itemize}

% ===================== SKILLS =====================
\section*{TECHNICAL SKILLS}
\textbf{Programming Languages:} Python, C++, C \\
\textbf{Cybersecurity:} VAPT, OSINT, Ethical Hacking, Web Security Fundamentals \\
\textbf{Tools \& Platforms:} Linux, Kali Linux, OpenCV, Git, Bash \\
\textbf{Core CS:} Data Structures \& Algorithms, Operating Systems, Computer Networks, DBMS

% ===================== EXPERIENCE =====================
\section*{EXPERIENCE}

\textbf{Cyber Warrior Intern, Gurugram Police Cyber Security Cell (GPCSSI 2025)} \hfill Jun 2025 -- Jul 2025
\begin{itemize}
  \item Worked on real-world cybercrime investigation workflows under the Gurugram Police Cyber Security Summer Internship.
  \item Developed a \textbf{Face Recognition System} using OpenCV to support identity verification tasks.
  \item Built a \textbf{Multiple IP Information Extractor} to automate OSINT-based IP intelligence collection.
  \item Performed \textbf{Vulnerability Assessment and Penetration Testing (VAPT)} on web applications.
  \item Received a \textbf{Letter of Recommendation} for technical contribution and execution quality.
  \item Awarded a \textbf{Letter of Appreciation from ACP, Cyber Crime (East Gurugram)} for project impact.
\end{itemize}

\textbf{Tech Lead, siNUsoid v9 Tech Fest \textbar{} NIIT University} \hfill Feb 2025 -- Nov 2025
\begin{itemize}
  \item Led the technical execution of the university’s annual tech fest platform across frontend and backend components.
  \item Coordinated a small tech team to deliver production-ready features under strict timelines.
  \item Oversaw deployments, issue resolution, and stability during live fest operations.
\end{itemize}

\textbf{Tech Team Volunteer, siNUsoid v8 Tech Fest \textbar{} NIIT University} \hfill Sep 2024 -- Nov 2024
\begin{itemize}
  \item Supported technical operations during the university’s annual science and technology fest.
  \item Assisted with live infrastructure, coordination, and issue resolution under production timelines.
  \item Received a \textbf{Certificate of Appreciation and Letter of Recommendation}.
\end{itemize}

% ===================== PROJECTS =====================
\section*{PROJECTS}

\textbf{Face Recognition System} \hfill Python / OpenCV
\begin{itemize}
  \item Implemented real-time face detection and recognition pipelines using OpenCV.
  \item Designed a lightweight identity-matching workflow suitable for investigative use cases.
\end{itemize}

\textbf{Multiple IP Information Extractor} \hfill Python / OSINT
\begin{itemize}
  \item Automated bulk IP intelligence collection using OSINT sources.
  \item Extracted geolocation, ISP, and network metadata for faster investigation triage.
\end{itemize}

\textbf{VAPT Program} \hfill Web Security
\begin{itemize}
  \item Conducted vulnerability scanning and penetration testing on web applications.
  \item Identified common misconfigurations and documented security weaknesses.
\end{itemize}

\textbf{Sinusoid v9 Fest Website (Frontend + Interactive UI)} \hfill Next.js / TypeScript / Three.js
\begin{itemize}
  \item Developed a student-facing website with modular architecture and performance-focused UI.
  \item Integrated interactive 3D components using React-Three-Fiber.
\end{itemize}

\textbf{Sinusoid CMS (Admin Panel)} \hfill React / Firebase / MUI
\begin{itemize}
  \item Extended and maintained an internal CMS used for event operations.
  \item Implemented data-heavy admin views using MUI DataGrid.
\end{itemize}

\textbf{Sinusoid Backend Services} \hfill Node.js / REST APIs
\begin{itemize}
  \item Maintained backend services supporting authentication and content delivery.
  \item Worked with environment-based configuration for controlled deployments.
\end{itemize}

\textbf{CTF Platform Backend (Abstruse v9)} \hfill Python
\begin{itemize}
  \item Collaborated on backend logic for Capture-The-Flag challenges.
  \item Focused on robustness and controlled challenge execution.
\end{itemize}

% ===================== ACHIEVEMENTS =====================
\section*{ACHIEVEMENTS}
\begin{itemize}
  \item Secured \textbf{2nd Place} in HackM Competitive Coding Competition, NIIT University (Cash Prize).
  \item Qualified for \textbf{Scaler National Coding League 2024} Regional Round.
\end{itemize}

% ===================== CERTIFICATIONS =====================
\section*{CERTIFICATIONS}
\begin{itemize}
  \item Gurugram Police Cyber Security Summer Internship (GPCSSI 2025)
  \item Ethical Hacking Course -- Udemy (Oct 2020)
  \item AI Aware -- Intel, CBSE \& Digital India (Jan 2022)
  \item Certificate of Participation -- 3-Day CS Workshop (NIIT University, Sept 2025)
\end{itemize}

% ===================== EDUCATION =====================
\section*{EDUCATION}
\textbf{NIIT University}, Neemrana, Rajasthan \\
B.Tech in Computer Science and Engineering \hfill 2024 -- 2028

\end{document}
